Cells at War: The Playfulness of Game-Based Learning

### 2023-04-05 cellsatwar_bus_presentation/beap_pres_dec.tex
BUS PRES DONE

% Title page details: 
\title[BEAP Dec 2022]{Cells at War: The Playfulness of Game-Based Learning} 
\author{Alexander Turco}
\date{April 5, 2023}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

	% Outline frame - SLIDE 2
	\begin{frame}{Overview}

		\begin{center}
		\begin{minipage}{6cm}

		  		\begin{block}{} \hyperlink{link1}{Background Information} \end{block}
		  		\begin{block}{} The Game Design Process \end{block}
		  		\begin{block}{} Collection of Student Feedback \end{block}
		  		\begin{block}{} Results \end{block}
		  		\begin{block}{} Conclusions \end{block}
		  		\begin{block}{} Future Work \end{block}

		\end{minipage}
		\end{center}

@@

	\begin{frame}{How Much Time Students Spend Playing Video Games}
		\begin{center}
		\includegraphics[width=11cm, height=7cm]{time_spent_playing_videogames.jpg}
		\end{center}
	\end{frame}

@@

	\begin{frame}{How Could Game-based Learning Help With the Following}
		\begin{center}
			\includegraphics[width=11cm, height=6cm]{how_does_gbl_help_in_science.jpg}
		\end{center}
	\end{frame}

@@

	\begin{frame}{If BIO1A03 Added a GBL Component, How Would it Improve Motivation to do the Following}
		\begin{center}
			\includegraphics[width=11cm, height=6cm]{ifbio1a03_added_gblcomponent.jpg}
		\end{center}
	\end{frame}

@@

	\section{Acknowledgements}
	\begin{frame}{Acknowledgements}
		Thank you...
		\begin{itemize}
			\item Dr. Rosa da Silva (McMaster)
			\item Jean Paul Amore (GBC)
			\item Bianca Flaim

		\end{itemize}
	\centering
	\includegraphics[width=5cm, height=3cm]{gbc.png}	
	\includegraphics[width=10cm, height=3cm]{cewil.jpg}
	\end{frame}

>>>>

% Title page details: 
\title[BEAP Dec 2022]{Cells at War: The Playfulness of Game-Based Learning} 
\author{Alexander Turco}
\date{April 13, 2023}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

	% Outline frame - SLIDE 2
	%\begin{frame}{Overview}

		%\begin{center}
		%\begin{minipage}{6cm}

		 % 		\begin{block}{} \hyperlink{link1}{Background Information} \end{block}
		  %		\begin{block}{} The Game Design Process \end{block}
		  %		\begin{block}{} Collection of Student Feedback \end{block}
		  %		\begin{block}{} Results \end{block}
		  		%\begin{block}{} Conclusions \end{block}
		  %		\begin{block}{} Future Work \end{block}

		%\end{minipage}
		%\end{center}

@@

	\begin{frame}{How Much Time Students Spend Playing Video Games}
		\begin{center}
		\includegraphics[width=11cm, height=7cm]{time_spent_playing_videogames.jpg}
		\begin{itemize}
			\item 44\% of students reported not playing video games at all
		\end{itemize}
		\end{center}
	\end{frame}

@@

	\begin{frame}{How Could Game-based Learning Help With the Following}
		\begin{center}
			\includegraphics[width=11cm, height=6cm]{how_does_gbl_help_in_science.jpg}
			\begin{itemize}
				\item 22\% increase in the number of respondants who felt that game-based learning would help connect their learning to societal/health related issues
			\end{itemize}
		\end{center}
	\end{frame}

@@

	\begin{frame}{If BIO1A03 Added a GBL Component, How Would it Improve Motivation to do the Following}
		\begin{center}
			\includegraphics[width=11cm, height=6cm]{ifbio1a03_added_gblcomponent.jpg}
			\begin{itemize}
				\item Overall increase in the number of students responding "very much" in all cases except memorizing course material
			\end{itemize}
		\end{center}
	\end{frame}

@@

	\section{Acknowledgements}
	\begin{frame}{Acknowledgements}
		\begin{columns}
			\begin{column}{0.45\textwidth}
				Thank you...
				\begin{itemize}
					\item Dr. Rosa da Silva
					\item Jean Paul Amore
					\item Bianca Flaim
					\item Oluwalonimi Ayekun
					\item Jennifer Luk
					\item The Entire George Brown College team
					\item CEWIL Canada	
				\end{itemize}
			\end{column}
			\begin{column}{0.5\textwidth}
				\centering
				\includegraphics[width=2cm, height=1cm]{gbc.png}	
				\includegraphics[width=5cm, height=2cm]{cewil.jpg}
			\end{column}
		\end{columns}
